During the pandemic, online communication and settings have become the norm for better management. School closures due to COVID-19 affected over 1.6 billion learners across 194 countries at the peak of closures in April 2020 according to UNESCO data. Despite efforts to reopen schools, the pandemic continues to disrupt education globally. Unfortunately, many universities still rely on traditional methods and do not effectively use online platforms for assigning tasks, submitting work, or enrolling in different semesters. To address this, a dynamic website will be developed to create easier access for both students and teachers. The web server will allow students to familiarize themselves with online tools and access information from a secured database, while supervisors can follow up on assigned tasks in a timely manner. Machine learning techniques will be used to create a comfortable experience for both users and administrators. The platform will also simplify examination and course evaluation, automating tasks and using advanced algorithms. Ultimately, the platform will serve as a common place for both teachers and students. The dynamic website will offer numerous benefits to students and teachers. For example, students will have access to all course materials and assignments online, making it easier to stay organized and manage their workload. They will be able to easily monitor student progress and assess performance, without the need for manual data entry or grading. The website will also enable them to communicate more effectively with students, providing an efficient channel for announcements, feedback, and questions. Teachers can also use the platform to share course materials and resources, making it easier for students to access and engage with content. By implementing machine learning techniques and advanced algorithms, the website will be able to adapt to the needs of both students and teachers. The website will help to mitigate the impact of the pandemic on education and enable students and teachers to continue to learn and grow.
\\
\vspace{3pt}
\textbf{Keywords:} Online platforms, Web-server, Students, Teachers, Tasks, Exam, Technology, Machine-learning
